descriptive anaysis

### 2020-06-18 src/bbData2020.Rmd
time series clustering time series plots literature YAMLchange for output dir

---
title: "descriptive anaysis"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

>>>>

---
title: "descriptive anaysis"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---
